Adaptative neighbouring methods applied to telephonic base stations

### 2024-08-21 article.tex
Correction fautes d'autrhaurgafe

\title{Adaptative neigbouring methods applied to telephonic base stations}
\author{\IEEEauthorblockN{Paul MÉHAUD}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
paul.mehaud@insa-rouen.fr}\\
\and
\IEEEauthorblockN{Brendan SÉVELLEC}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
brendan.sevellec@insa-rouen.fr}}

@@

\section{Reminder on existing methods\label{sec:reminder}}
    \subsection{Finding potential neighbours}
        When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
        For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

@@

        \subsubsection{Quadrant criterion}
            As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the $k$-NN potential neigbours method.

@@

    \subsection{Density-based clustering methods}
        \subsubsection{\acrshort{dbscan}}
            \acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
            \begin{itemize}
                \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
                \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
            \end{itemize}

@@

            In other words, it tends to select the angle with which the potential neighbors are as much in the middle of their respective quadrants as possible.

@@

\section{Results}

    \subsection{Measurement of \acrshort{bs} density}

>>>>

\title{Adaptative neighbouring methods applied to telephonic base stations}
\author{\IEEEauthorblockN{Paul MÉHAUD}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
paul.mehaud@insa-rouen.fr}\\
\and
\IEEEauthorblockN{Brendan SÉVELLEC}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
brendan.sevellec@insa-rouen.fr}}

@@

\section{Reminder on existing methods\label{sec:reminder}}
    \subsection{Finding potential neighbours}
        When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
        For that, we will construct a neighbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

@@

        \subsubsection{Quadrant criterion}
            As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the $k$-NN potential neighbours method.

@@

    \subsection{Density-based clustering methods}
        \subsubsection{\acrshort{dbscan}}
            \acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
            \begin{itemize}
                \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
                \item \emph{$n_{\text{min}}$}: The shortest number of neighbours a points needs to have to be considered as a core point of a cluster.
            \end{itemize}

@@

            In other words, it tends to select the angle with which the potential neighbours are as much in the middle of their respective quadrants as possible.

@@

\section{Results}
    \subsection{Measurement of \acrshort{bs} density}
